The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-02-04 repeater-vladata.tex
rework intro, lensing, energy disn

\begin{abstract}
The recent precision localization of \frb\ has helped identify its host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical source. We present results of the coordinated observing campaign that made this localization, including the first simultaneous detection of an FRB burst with multiple telescopes. Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories, and one was detected by the Arecibo Observatory at 1.4~GHz. We show that the burst spectra typically have a broad shape that tapers off on scales of $\sim500$~MHz, plus fine spectral structure on MHz-frequency scales. We present the first FRB energy distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb. **This source shows that optimal FRB survey strategies should...**
\end{abstract}

\section{Introduction}
Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[DM; ][]{2007Sci...318..777L}. Their large DM implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}. Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}. However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.

This paper is part of a series that presents the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position demonstrating that it repeats \citep{2016Natur.531..202S}. Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it to (RA, Dec) of (05h31m58.70s, +33d08m52.5s) with a precision of 0.1\arcsec. Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a redshift of 0.193 with a precision of 0.01" \citep[$\sim40$\ pc]{OPT, EVN}.

\frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance. Its lookback and luminosity distances are 746 and 972 Mpc, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}. This association means that \frb\ is orders of magnitude more luminous than any other millisecond transient and that its DM traces both the host and intergalactic medium \citep{OPT}. The promise implied by the first reported FRB \citep{2007Sci...318..777L} is now being realized.

The confirmation of a cosmological distance for \frb\ could have wide-ranging implications for the FRB population as a whole. If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies. However, it has not been demonstrated that \frb\ is representative of the overall FRB population. In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative. An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}. The repeating nature of \frb\ provides us with a sample of bursts covering a range of spectral properties, temporal properties, and luminosities that can be used to test its connection to the larger FRB population.

We can also assume that \frb\ is representative of all FRBs and use it to constrain the physical processes at play in the overall FRB population. In this case, we know that FRBs are apparently luminous, but it is not yet clear what processes are responsible. Possibilities include intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}. The paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories. The repetition of \frb\ also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.

@@

\begin{figure*}[t]
\begin{center}
\includegraphics[width=2\columnwidth]{timeline}
\caption{Summary of observing coverage and detections of \frb\ during the multi-telescope observing campaign in August and September 2016. Symbols show days with observations and circles highlight observations that detected bursts from \frb. Multiple circles indicate multiple burst detections, except for Arecibo, which typically has multiple detections per observing session (a detailed analysis is left for a future paper). The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes. The solid black line shows the simultaneous burst detection at VLA and Arecibo.
\label{fig:multi}}
\end{center}
\end{figure*}

@@

\subsubsection{Spectral Modeling}
\label{sec:spec}
We used two techniques to refine the analysis of the nine VLA radio burst spectra described in \citet{LOC}. First, we improved on the initial analysis by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$). After calibration and flagging, the visibility phases were rotated to the best-fit location to extract a Stokes I spectrum that maximizes the image S/N for each burst. Table \ref{tab:spec} gives the resulting integrated burst flux density, image S/N, and Stokes V, while Figure \ref{fig:spec} shows the Stokes I spectra. Generally, the burst spectra are characterized by a broad, Gaussian shape with inter-channel modulation as high as 100\%.

@@

**Does channel-scale structure only appear around 3~GHz?**

@@

\subsection{Energy and Brightness Distribution}
\label{sec:disn}
Knowing the burst distance, we calculate their total energy by integrating flux in time and frequency (Table \ref{tab:spec}). The VLA burst spectra suggest that some bursts may be contained by the 2.5 to 3.5~GHz band. If those bursts truly only emit in this band, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.

This uniform sample of burst energies can be used to infer more general properties of \frb. We treat the detection probability as a Poisson process with a rate that scales with the energy as a powerlaw. Figure \ref{fig:lumd} shows the probability distribution for the powerlaw amplitude and index for the sample of nine VLA bursts. The energy powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4; for a cumulative energy distribution, this corresponds to a powerlaw index of roughly --0.6. The flatness of the distribution is also clear from range of significance of the nine bursts (12 to 179$\sigma$). All bursts are much brighter than the sensitivity limit, so the distribution is not affected by a completeness limit. **elaborate on limit and completeness**

@@

\includegraphics[width=0.9\columnwidth]{luminosity_disn}
\caption{\emph{Top:} Cumulative energy distribution with powerlaw fit for the nine VLA bursts from \frb. \emph{Bottom:} Probability distribution of energy model of the differential luminisotiy distribution. The powerlaw is referenced to $L=2\times10^{38}$\ erg.
\label{fig:lumd}}
\end{center}
\end{figure}

@@

@@

\subsection{Emission Physics and Burst Energetics}
**compare to crab GP energy and Tb** **how to scale it up?**

The measurement of a redshift to the host of \frb\ allows us to measure the burst luminosity and energy. We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo. This confirms the results presented in \citet{LOC}, which quoted a energy on the order of $10^{38}$\ erg. The more refined analysis presented here results in somewhat higher burst fluxes, so the brightest VLA burst energy ranges as high as $5\times10^{39}$\ erg.

However, the total energy emitted by \frb\ can be orders of magnitude different than this isotropic, apparent energy. While the emission process is not yet known, it is neccessarily coherent \citep{2016Natur.531..202S, WEIRD}, so relativistical beaming will amplify the apparent brightness. Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways \citep{CORDES} and the duration of the emission in the source frame is not known. In any case, the energy scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.

\subsection{FRB Flux Distribution}
The first FRB detection (``Lorimer burst'') was surprising for its unusually high brightness with a lack of lower-significance detections. With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}. This fact was recently demonstrated by yet another detection of an extremely bright FRB \citep{2016arXiv161105758R}.

@@

>>>>

\begin{abstract}
The recent precision localization of \frb\ has helped identify its host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical source. We present results of the coordinated observing campaign that made this localization, including the first simultaneous detection of an FRB burst with multiple telescopes. Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories, and one was detected by the Arecibo Observatory at 1.4~GHz. We show that the burst spectra typically have a broad shape that tapers off on scales of $\sim500$~MHz, plus fine spectral structure on MHz-frequency scales. We present the first FRB energy distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb. 
*population models* *slsn*
**This source shows that optimal FRB survey strategies should...**
\end{abstract}

\section{Introduction}

Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[the ``Lorimer burst'';][]{2007Sci...318..777L}. Their large dispersion measure (DM) implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}. Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}. However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.

This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position demonstrating that it repeats \citep{2016Natur.531..202S}. Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec. Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a redshift of 0.193 with a precision of 0.01" \citep[$\sim40$\ pc]{OPT, EVN}.

\frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance. Its lookback and luminosity distances are 746 and 972 Mpc, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}. This association means that \frb\ is orders of magnitude more luminous than any other millisecond transient and that its DM traces both the host and intergalactic medium \citep{OPT}. If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies. Thus, the confirmation of a cosmological distance for \frb\ has begun to fulfil the promise implied by the Lorimer burst.

Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, we still do not know what causes them. 
**magnetar birth?**
Also, it has not been demonstrated that \frb\ is representative of the overall FRB population. In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative. An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}. The repeating nature of \frb\ provides us with a sample of bursts covering a range of spectral properties, temporal properties, and luminosities that can be used to test its connection to the larger FRB population.

We can also assume that \frb\ is representative of all FRBs and use it to constrain the physical processes at play in the overall FRB population. In this case, we know that FRBs are apparently luminous, but if that is due to intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}. The paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories. The repetition of \frb\ also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.

@@

\begin{figure*}[t]
\begin{center}
\includegraphics[width=2\columnwidth]{timeline}

\includegraphics[width=2\columnwidth]{timeline}

\includegraphics[width=2\columnwidth]{timeline}
\caption{Summary of coverage and detections of \frb\ during the the three VLA observing campaigns
 %multi-telescope observing campaign in August and September 2016. 
Symbols show days with observations and circles highlight observations that detected bursts from \frb. Multiple circles indicate multiple burst detections, except for Arecibo, which typically has multiple detections per observing session (a detailed analysis is left for a future paper). The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes. The solid black line shows the simultaneous burst detection at VLA and Arecibo.
\label{fig:multi}}
\end{center}
\end{figure*}

@@

\subsubsection{Spectral Modeling}
\label{sec:spec}
We used two techniques to refine the analysis of the nine VLA radio burst spectra described in \citet{LOC}. First, we improved on the initial analysis by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$). After calibration and flagging, the visibility phases were rotated to the best-fit location \citep[(RA, Dec) $=$ (05h31m58.70s, +33d08m52.5s);][]{LOC} to extract a Stokes I spectrum that maximizes the image S/N for each burst. Table \ref{tab:spec} gives the resulting integrated burst flux density, image S/N, and Stokes V, while Figure \ref{fig:spec} shows the Stokes I spectra. Generally, the burst spectra are characterized by a broad, Gaussian shape with inter-channel modulation as high as 100\%.

@@

%**Does channel-scale structure only appear around 3~GHz?**

@@

\subsection{Energy and Brightness Distribution}
\label{sec:disn}
Knowing the burst distance, we calculate their total energy by integrating flux in time and frequency (Table \ref{tab:spec}). The VLA burst spectra suggest that some bursts may be contained by the 2.5 to 3.5~GHz band. If those bursts only emit in this band, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties. We proceed under this assumption here and discuss caveats later.

The \frb\ burst energy distribution is relatively flat, as seen in the range of significance of the nine bursts (12 to 179$\sigma$). All bursts are much brighter than the sensitivity limit ($8\sigma$) and data quality are relatively uniform and good, so the distribution is not affected by a completeness limit.

We visualize and model the burst energy distribution in two ways. First, the top panel of Figure \ref{fig:lumd} shows the \emph{cumulative} energy distribution and its best-fit powerlaw index of --0.6. Second, we use probabilistic modeling to the energies to quantify it directly. We model the energy distribution as a Poisson probability with rate function $\lambda=a\ E^\alpha$. Figure \ref{fig:lumd} shows the probability distribution for the powerlaw amplitude and index for the sample of nine VLA bursts. The energy powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4.

@@

\includegraphics[width=0.9\columnwidth]{luminosity_disn}
\caption{\emph{Top:} Cumulative energy distribution with powerlaw fit for the nine VLA bursts from \frb. \emph{Bottom:} Probability distribution of energy model of the differential luminisotiy distribution. The powerlaw is referenced to $L=3\times10^{38}$\ erg.
\label{fig:lumd}}
\end{center}
\end{figure}

**Does this flat distribution explain FRB flux flatness?**

@@

**caveats of S-band assumption**

@@

\subsection{Emission Physics and Burst Energetics}
The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg. We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo. \frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}\ erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K]{2003Natur.422..141H,2014PhRvD..89j3009K}. While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.

Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways and the duration of the emission in the source frame is not known \citep{2016arXiv160505890C}. \citet{CORDES} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of mangitude. That model argues that the simultaneous appearance of a burst from 1.2 to 3.5~GHz requires a lens with the focal frequency be $\gtrsim 3.5$~GHz. This gives a constraint on the combination $\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$, where $DM_0$, $a$, and $d_*$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively. A lens placed at $d_{sl}\approx1$~kpc is consistent with typical properties of the interstellar medium. Lenses that are influenced by the source would be much nearer to the source $d_{\sl} \ll 1$~kpc, requiring large values of ${\rm DM_0 / a_{\rm AU}^2$.

\subsection{FRB Flux Distribution}
The Lorimer burst was surprising for its unusually high brightness with a lack of lower-significance detections. With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}. This fact was recently demonstrated by yet another detection of an extremely bright FRB \citep{2016arXiv161105758R}.

@@

FRBs like SGRs? 2016ApJ...826..226K
